External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-15 CVPR2017_Review_Unified.tex
a

\vspace{-2mm}
\subsubsection{Guided Orthogonal Dictionary Learning}

@@

We let the orthogonal dictionary $\mathbf{D}_{k}$ be $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,\text{E}}\ \mathbf{D}_{k,\text{I}}]\in \mathbb{R}^{3p^2\times 3p^2}$, where $\mathbf{D}_{k,\text{E}}=\mathbf{U}_{k}(:,1:r)\in\mathbb{R}^{3p^2\times r}$ is the external sub-dictionary and it includes the first $r$ most important eigenvectors of $\mathbf{U}_{k}$, and the internal sub-dictionary $\mathbf{D}_{k,\text{I}}$ is to be adaptively learned from the noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.\ The rationale to design $\mathbf{D}_{k}$ as a hybrid dictionary is as follows.\ The external sub-dictionary $\mathbf{D}_{k,\text{E}}$ is pre-trained from external clean data, and it represents the $k$-th latent subspace of natural images, which is helpful to reconstruct the common latent structures of images. However, $\mathbf{D}_{k,\text{E}}$ is general to all images and it is not adaptive to the given noisy image.\ Some fine-scale details specific to the given image may not be well characterized by $\mathbf{D}_{k,\text{E}}$. Therefore, we learn an internal sub-dictionary $\mathbf{D}_{k,\text{I}}$ to supplement $\mathbf{D}_{k,\text{E}}$.\ In other words, $\mathbf{D}_{k,\text{I}}$ is to reveal the latent subspace adaptive to the input noisy image, which cannot be effectively represented by $\mathbf{D}_{k,\text{E}}$.

>>>>

\vspace{-3mm}
\subsubsection{Guided Orthogonal Dictionary Learning}

@@

We let the orthogonal dictionary $\mathbf{D}_{k}$ be $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,\text{E}}\ \mathbf{D}_{k,\text{I}}]\in \mathbb{R}^{3p^2\times 3p^2}$, where $\mathbf{D}_{k,\text{E}}=\mathbf{U}_{k}(:,1:r)\in\mathbb{R}^{3p^2\times r}$ is the external sub-dictionary and it includes the first $r$ most important eigenvectors of $\mathbf{U}_{k}$, and the internal sub-dictionary $\mathbf{D}_{k,\text{I}}\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is to be adaptively learned from the noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.\ The rationale to design $\mathbf{D}_{k}$ as a hybrid dictionary is as follows.\ The external sub-dictionary $\mathbf{D}_{k,\text{E}}$ is pre-trained from external clean data, and it represents the $k$-th latent subspace of natural images, which is helpful to reconstruct the common latent structures of images. However, $\mathbf{D}_{k,\text{E}}$ is general to all images and it is not adaptive to the given noisy image.\ Some fine-scale details specific to the given image may not be well characterized by $\mathbf{D}_{k,\text{E}}$. Therefore, we learn an internal sub-dictionary $\mathbf{D}_{k,\text{I}}$ to supplement $\mathbf{D}_{k,\text{E}}$.\ In other words, $\mathbf{D}_{k,\text{I}}$ is to reveal the latent subspace adaptive to the input noisy image, which cannot be effectively represented by $\mathbf{D}_{k,\text{E}}$.
